Journal

### 2024-11-15 Journal/notes.tex
Update in direction of research

>>>>

Ideas to address:
\begin{itemize}
  \item Since the current static ETM matches the minimum feasible ROA we could think of some other ETM mechanism. To be clearer the quadratic constraints of the non-linearities of the activation functions are mandatory and cannot be neglected. Since the static ETM uses the exact same conditions It is clear that the ROA will be the same. 
  \item One possible criteria to try and obtain with an ETM is something regarding the inter-event period and the preferred direction to preserve in ROA shrinking. In particular the direction around $\theta$ since the addition of the integrator in the dynamics makes the system more stable in that direction. Some work of Sophie should have addressed something similar. As regards the inter-event period look at some work of Antoine Girard.
  \item Another possible improvement is changing the quadratic constraints whenever we have some fixed matrices like the one used to address the $sin(\theta) - \theta$ non-linearity. It sees the addition of new variables and constraints to the LMI like seen in the two \textit{k-contraction} papers of Samuele.
  \item The last idea is to try and find a way to implement multiple objectives in the LMI. There are some papers to take idea from like in \cite{multiobjective-1} and \cite{multiobjective-2}.
\end{itemize}
